<!-- 
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Single study data} 
-->
---
title: "Hozo et al. Replication"
author: "Charles T. Gray"
date: `r dontpanic::title_date()`
vignette: >
  %\VignetteIndexEntry{Hozo replication}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

dontpanic::nix()
library(tidyverse)

```

# Tasks

- Referencing
- Import Hozo estimator
- Graphed the relative error vs sample size. (Here I'm assuming that by relative error, they mean $\frac {\widehat\mu - \mu} \mu$ - or is it $\frac {\mu - \widehat\mu} \mu$?) - Investigate. Could be absolute value, too. 

# Objective

We want to replicate the simulations presented in Hozo et al.'s paper. 

# Theoretically, what did they do?

- Drew 200 samples of sizes ranging from 8 to 100. (*From memory, I think they increase in increments of 2.*)
- N$(50, 17^2)$, LN$(4, 0.3)$, Beta$(9,4)$, Exp$(10)$, Weibull$(2, 35)$.
- Graphed the relative error vs sample size. (Here I'm assuming that by relative error, they mean $\frac {\widehat\mu - \mu} \mu$ - or is it $\frac {\mu - \widehat\mu} \mu$? It could even be absolute, will need to check.)

# Estimators

## For the sample mean

- Equation (5)
- Median

## For the sample standard deviation

- Equation (16)
- range$/4$
- range$/6$

# Generate data

I'll use some functions from my helper functions package `dontpanic`. 
```{r}
hozo_sim <- tibble(dist = list( # I love this function.
  list(rdist = "norm",
       rpars = list(mean = 50, sd = 17)),
  list(rdist = "lnorm",
       rpars = list(meanlog = 4, meansd = 0.3)),
  list(rdist = "beta",
       rpars = list(9, 4)),
  list(rdist = "exp",
       rpars = 10),
  list(rdist = "weibull",
       rpars = c(2, 35))
)) %>% 
  mutate( # Calculate true mean and sd.
    true_mean = map2_dbl(
      map_chr(dist, "rdist"),
      map(dist, "rpars"),
      .f = dontpanic::get_mean
    ),
    true_sd = pmap_dbl(
      list(
      map_chr(dist, "rdist"),
      map(dist, "rpars"),
      true_mean
      ),
      .f = dontpanic::get_sd
    ),
    rdist = map_chr(dist, "rdist"),
    rpars = map(dist, "rpars")
  ) %>% 
  select(-dist) %>% 
  mutate(
    sim_pars = pmap(list(rdist, rpars, true_mean, true_sd), list)
  ) %>% 
  select(sim_pars)
  
```

## Get samples 

```{r Get samples}

hozo_sim <- cross(
  list(sim_pars = hozo_sim$sim_pars,
       n = seq(1, 12, by = 2))
)

# Convert to tibble.
hozo_sim <- tibble(
  rdist = map_chr(hozo_sim, c(1,1)),
  rpars = map(hozo_sim, c(1,2)),
  true_mean = map_dbl(hozo_sim, c(1,3)),
  true_sd = map_dbl(hozo_sim, c(1, 4)),
  n = map_dbl(hozo_sim, "n")
)  %>% # Generate samples from parameters.
  mutate(sample = pmap(list(n = n, dist = rdist, par = rpars), 
                       dontpanic::get_sample)) %>% 
  mutate( # Calculate summary statistics.
    min = map_dbl(sample, min),
    first_q = map_dbl(sample, quantile, p = 0.25),
    median = map_dbl(sample, median),
    third_q = map_dbl(sample, quantile, p = 0.75),
    max = map_dbl(sample, max)
  )


  # Not sure I need parameters as variables.
  # mutate(
  #   rpar1 = map_dbl(rpars, 1),
  #   rpar2 = map_dbl(rpars, 2, .default = NA) 
  # ) 

# Take a look.
hozo_sim %>% listviewer::jsonedit()

```

## Apply estimators

```{r Estimators}
hozo_sim <- hozo_sim %>% 
  mutate(
    ran_4 = (max - min) / 4, 
    ran_6 = (max - min) / 6
  ) 


```

