<!-- 
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Single study data} 
-->
---
title: "Hozo et al. Replication"
author: "Charles T. Gray"
date: `r dontpanic::title_date()`
vignette: >
  %\VignetteIndexEntry{Hozo replication}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

dontpanic::nix()
library(tidyverse)

```

# Tasks

- Referencing
- Import Hozo estimator
- Graphed the relative error vs sample size. (Here I'm assuming that by relative error, they mean $\frac {\widehat\mu - \mu} \mu$ - or is it $\frac {\mu - \widehat\mu} \mu$?) - Investigate.


# Objective

We want to replicate the simulations presented in Hozo et al.'s paper. 

# Theoretically, what did they do?

- Drew 200 samples of sizes ranging from 8 to 100. (*From memory, I think they increase in increments of 2.*)
- N$(50, 17^2)$, LN$(4, 0.3)$, Beta$(9,4)$, Exp$(10)$, Weibull$(2, 35)$.
- Graphed the relative error vs sample size. (Here I'm assuming that by relative error, they mean $\frac {\widehat\mu - \mu} \mu$ - or is it $\frac {\mu - \widehat\mu} \mu$? It could even be absolute, will need to check.)

# Estimators

## For the sample mean

- Equation (5)
- Median

## For the sample standard deviation

- Equation (16)
- range$/4$
- range$/6$

# Generate data

I'll use some functions from my helper functions package `dontpanic`. 
```{r Get samples}
hozo_sim <- cross(list(dist = list( # I love this function.
  list(rdist = "norm",
       rpars = list(mean = 50, sd = 17)),
  list(rdist = "lnorm",
       rpars = list(meanlog = 4, meansd = 0.3)),
  list(rdist = "beta",
       rpars = list(9, 4)),
  list(rdist = "exp",
       rpars = 10),
  list(rdist = "weibull",
       rpars = c(2, 35))
),
n = seq(1, 10, by = 2)))

# Convert to tibble.
hozo_sim <- tibble(
  rdist = map_chr(hozo_sim, c("dist", "rdist")),
  rpars = map(hozo_sim, c("dist", "rpars")),
  n = map_dbl(hozo_sim, "n")
)  %>% # Generate sampes from parameters.
  mutate(sample = pmap(list(n = n, dist = rdist, par = rpars), 
                       dontpanic::get_sample)) %>% 
  mutate( # Calculate summary statistics.
    min = map_dbl(sample, min),
    first_q = map_dbl(sample, quantile, p = 0.25),
    median = map_dbl(sample, median),
    third_q = map_dbl(sample, quantile, p = 0.75),
    max = map_dbl(sample, max)
  )


  # Not sure I need parameters as variables.
  # mutate(
  #   rpar1 = map_dbl(rpars, 1),
  #   rpar2 = map_dbl(rpars, 2, .default = NA)
  # ) 

# Take a look.
hozo_sim %>% listviewer::jsonedit()

```


