---
title: "Other methods coverage"
author: "Trouble"
date: "11/11/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library(tidyverse)

```


# Tasks

- ~~Load data from my `metamedian` package.~~
- ~~Calculate estimates of the mean and standard deviation using the various estimators.~~
- Convert to longform. 
- Calculate confidence intervals.
- Calculate absolute relative bias.
- Calculate relative interval width. 
- Consider results; do I need to check the estimator functions carefully?
- Wasn't there some horrible issue with the medians?
- Calculate absolute bias to compare relative absolute bias.
- Rotate $x$-axis.
- Change legend names to mathematics.

# Objective

Reproduce the coverage probabiltiy plots. 

# Simulation

```{r Get data}
om_sim <- metamedian::ss_data %>% # Load data from metamedian pkg.
  filter(arm_adj == "sample_stats_2_null") %>%
  mutate( # Now for the estimates.
    hozo = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_hozo(
          a = summary_tibble$min,
          m = summary_tibble$median,
          b = summary_tibble$max,
          n = summary_tibble$n
        )
      }
    ),
    bland = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_bland(
          a = summary_tibble$min,
          q.1 = summary_tibble$first_q,
          m = summary_tibble$median,
          q.3 = summary_tibble$third_q,
          b = summary_tibble$max,
          n = summary_tibble$n
        )
      }
    ),
    wan_c1 = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_wan_c1(
          a = summary_tibble$min,
          m = summary_tibble$median,
          b = summary_tibble$max,
          n = summary_tibble$n
        )
      }
    ),
    wan_c2 = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_wan_c2(
          a = summary_tibble$min,
          q.1 = summary_tibble$first_q,
          m = summary_tibble$median,
          q.3 = summary_tibble$third_q,
          b = summary_tibble$max,
          n = summary_tibble$n
        )
      }
    ),
    wan_c3 = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_wan_c3(
          q.1 = summary_tibble$first_q,
          m = summary_tibble$median,
          q.3 = summary_tibble$third_q,
          n = summary_tibble$n
        )
      }
    )
  )

```

```{r Long form}
om_sim <- om_sim %>% 
  gather(key = "method",
         value = "effects",
         hozo, bland, wan_c1, wan_c2, wan_c3)


```


```{r Confidence intervals}
om_sim <- om_sim %>%
  mutate(
    ci_lb = map_dbl(effects, "centre") - qnorm(0.975) * map_dbl(effects, "se"),
    ci_ub = map_dbl(effects, "centre") + qnorm(0.975) * map_dbl(effects, "se"),
    true_in = pmap_lgl(
      .l = list(lb =
                  ci_lb,
                ub = ci_ub,
                true_mean = true_mean),
      .f = function(lb, ub, true_mean) {
        lb < true_mean & true_mean < ub
      }
    ),
    relative_interval_width = (ci_ub - ci_lb) / true_mean,
    relative_absolute_bias = abs(true_mean -
                                   map_dbl(effects,
                                           "centre") /  true_mean)
  )
```

```{r Calculate coverage}


om_means <- om_sim %>%
  group_by(n, rdist, rpar1, method) %>%
  summarise(
    ci_lb = mean(ci_lb),
    ci_ub = mean(ci_ub),
    coverage = sum(true_in) / metamedian::ss_par[[2]],
    relative_interval_width = mean(relative_interval_width),
    relative_absolute_bias = mean(relative_absolute_bias)
  )

```

```{r Plot}
cov_dist <- om_means %>%
  ggplot(aes(x = rdist,
             y = coverage)) +
  geom_point(aes(colour = relative_absolute_bias,
                 size = relative_interval_width)) +
  facet_grid(n ~ method)

```

```{r Save objects to package}
devtools::use_data(cov_dist, overwrite = T)

```

