---
title: "Other methods coverage"
author: "Trouble"
date: "11/11/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library(tidyverse)

```


# Tasks

- ~~Load data from my `metamedian` package.~~
- ~~Calculate estimates of the mean and standard deviation using the various estimators.~~
- Convert to longform. 
- Calculate confidence intervals.
- Calculate absolute relative bias.
- Calculate relative interval width. 
- Consider results; do I need to check the estimator functions carefully?
- Wasn't there some horrible issue with the medians?

# Objective

Reproduce the coverage probabiltiy plots. 

# Simulation

```{r Get data}
om_sim <- metamedian::ss_data %>% # Load data from metamedian pkg.
  mutate( # Now for the estimates.
    hozo_effects = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_hozo(
          a = summary_tibble$min,
          m = summary_tibble$median,
          b = summary_tibble$max,
          n = summary_tibble$n
        )
      }
    ),
    bland_effects = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_bland(
          a = summary_tibble$min,
          q.1 = summary_tibble$first_q,
          m = summary_tibble$median,
          q.3 = summary_tibble$third_q,
          b = summary_tibble$max,
          n = summary_tibble$n
        )
      }
    ),
    wan_effects_c1 = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_wan_c1(
          a = summary_tibble$min,
          m = summary_tibble$median,
          b = summary_tibble$max,
          n = summary_tibble$n
        )
      }
    ),
    wan_effects_c2 = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_wan_c2(
          a = summary_tibble$min,
          q.1 = summary_tibble$first_q,
          m = summary_tibble$median,
          q.3 = summary_tibble$third_q,
          b = summary_tibble$max,
          n = summary_tibble$n
        )
      }
    ),
    wan_effects_c3 = map(
      sample_stats_1,
      .f = function(summary_tibble) {
        metamean::eff_est_wan_c3(
          q.1 = summary_tibble$first_q,
          m = summary_tibble$median,
          q.3 = summary_tibble$third_q,
          n = summary_tibble$n
        )
      }
    )
  )

```

